## Activity log

```{r, echo=FALSE}
hour <- 60*60*1000   # milliseconds per hour
day <- 24*hour       # milliseconds per day

to.time <- function(unix.ms) {
  as.POSIXct(as.numeric(as.vector(unix.ms))/1000, origin="1970-01-01 GMT", tz="GMT")
}

# Note: occasionally, activity.log becomes corrupted (due to a killed process)
# and needs to be manually cleaned up (by deleting an invalid line).
read.activity <- function() {
  activity.data <- read.table(file("data/activity.log"), header=FALSE, sep="\t", fill=TRUE, col.names=c("time.raw", "action", "entity1", "entity2"))
  time <- to.time(activity.data$time.raw)
  activity.data <- subset(activity.data, !is.na(time))
  activity.data <- data.frame(activity.data, time=to.time(activity.data$time.raw))
}

activity <- read.activity()
activity <- activity[with(activity, order(time)),]
time <- activity$time
diff <- find.increments(time)
```

By default, SmSn Server maintains an ongoing record of editing and viewing activity in a file called `activity.log`. From this log, a great deal of information can be gleaned on temporal patterns of activity level, topics, and sentiment.

Note: the activity log is typically a large file (megabytes to tens of megabytes), and may take a while to load. It may also require manual cleanup in the case of abnormal program termination.

### Continuity

```{r, echo=FALSE}
```

The plot below shows the gaps between successive actions in the activity log. Any long periods of inactivity (or loss of activity data) should be visible here.

```{r, echo=FALSE}
renderPlot({
  plot(x=time[1:(length(time)-1)], y=diff, type="l", log="y", ylim=c(1, max(diff)),
    xlab="event time", ylab="time between events (s)", main="activity gaps by time")
})
```

### Entity frequency

```{r, echo=FALSE}
e1 <- as.vector(activity$entity1)
e2 <- as.vector(activity$entity2[sapply(as.vector(activity$entity2), function(s){nchar(s) > 0})])
e <- c(e1, e2)
t <- table(e)

mean.events.per.entity <- mean(t)
sd.events.per.entity <- sd(t)

logmean <- mean(log(t))
logsd <- sd(log(t))
```

Most entities in the graph are the subject of repeated activity.
In the current graph, the average entity has been edited **`r num(mean.events.per.entity)` times** (&sigma;=`r num(sd.events.per.entity)`).
In graphs studied thus far, frequency follows a [log-normal distribution](https://en.wikipedia.org/wiki/Log-normal_distribution) with &mu;=`r num(logmean)` and &sigma;=`r num(logsd)`.

```{r, echo=FALSE}
tl <- as.vector(t[t <= 100])
renderPlot({
  plot(hist(tl, breaks=100),
    xlab="number of events",
    ylab="number of entities",
    main="frequency of activity by entity")
  abline(col="red", v=logmean)
  abline(col="blue", v=mean.events.per.entity)
})
```

The mode of the distribution is indicated with a <span style="color:red">red line</span>, while the mean is indicated with a <span style="color:blue">blue line</span>.
