## @alias property

```{r, echo=FALSE}
aliases <- sapply(as.vector(entities$alias), as.character)
alias.lengths <- sapply(aliases, nchar)
alias.entities <- entities[alias.lengths > 0,]
unique.aliases <- unique(alias.entities$alias)
total.alias.entities <- nrow(alias.entities)
```

The `@alias` property provides an external identity for an entity, such as a [URI](https://en.wikipedia.org/wiki/Uniform_Resource_Identifier). For example, the entity representing Saturn might given an alias of `https://en.wikipedia.org/wiki/Saturn`, linking it with the Wikipedia page for the planet Saturn.

In the current data set, there are **`r num(total.alias.entities)` entities** `r perc.of.entities(nrow(alias.entities))` with a non-empty alias.

### Duplicate aliases

```{r, echo=FALSE}
df <- data.frame(alias=subset(data.frame(entities, d=duplicated(entities$alias), l=nchar(as.vector(entities$alias))), l > 0 & d == TRUE)$alias)
dup.alias.entities <- merge(df, entities, by="alias")
count.dupes <- nrow(dup.alias.entities)
```

Duplicate alias values are to be avoided; in most cases, two entities which share an alias should be the same entity (i.e. should also have the same id).
In the current graph, there are **`r num(count.dupes)` entities** `r perc.of.entities(count.dupes)` with non-unique aliases, sharing a total of **`r num(length(unique(dup.alias.entities$alias)))`** aliases overall.

### Alias domains

```{r, echo=FALSE}
library(urltools)

is.http.uri <- function(s) {substr(s, 1, 4) == "http"}
uris <- unique.aliases[sapply(unique.aliases, is.http.uri)]
domains <- sapply(uris, domain)
```

`@alias` values are not necessarily HTTP URIs, but many of them are; aliases are often used as bookmarks, linking to resources on the Web. Below are the domains of HTTP or HTTPS URI aliases in the current graph, ranked by frequency.

```{r, echo=FALSE}
showFreqTable(domains, FALSE)
```

<!--
#########################################
# distance from DBpedia-linked atoms

v <- read.table(file("/tmp/joshkb-vertices.tsv"), header=TRUE, sep="\t", quote="", comment.char="")
e <- read.table(file("/tmp/joshkb-edges.tsv"), header=TRUE)
d <- subset(v, substr(alias, 1, 28) == "http://dbpedia.org/resource/")

did <- d$id

merge.dbpedia.ids <- function(id) {
    if (id %in% did) "DBPEDIA" else id
}

# note: this takes much longer without as.vector
e.merged <- data.frame(
    from=sapply(as.vector(e$from), merge.dbpedia.ids),
    to=sapply(as.vector(e$to), merge.dbpedia.ids))

from <- sapply(e$from, merge.dbpedia.ids)

library(igraph)

g <- graph.data.frame(e.merged)

# confirm that this is the "DBPEDIA" vertex
V(g)[1]

vs <- as.vector(c(1))
sp <- shortest.paths(g, v=vs)

df <- data.frame(len=as.vector(sp-1))
df <- subset(df, len >= 0)

t <- table(df$len)
display <- c(nrow(d), t[2:length(t)])
pdf("/tmp/steps-from-dbpedia-atoms.pdf", width=5, height=2)
par(mar=c(2,5,2,1.5))
barplot(display, ylab="total atoms")
dev.off()

# TODO: is.inf?
df2 <- subset(df, len <= 100)
t2 <- table(df2)
totals <- c(nrow(d), t2[2:length(t2)])
[0:(length(totals)+1)]*totals

# hmm, why are we missing 14% of vertices?
sum(totals)/nrow(v)

# anyway, we'll call it 2.35 steps on average
s <- sum((0:(length(totals)-1))*totals)
s / sum(totals)

# TODO: is.inf?
mean(subset(df, len <= 100)$len)
-->



