## Git history

```{r}
git.log.file <- "data/git-log.csv"
git <- read.csv(file(git.log.file), header=FALSE)

timestamp <- {}
commit <- {}
committer <- {}
last.timestamp <- -1
last.commit <- ""
last.committer <- ""
for (i in c(1:nrow(git))) {
  if (git$V2[i] == "COMMIT") {
    last.timestamp <- git$V5[i]
    last.commit <- as.character(git$V3[i])
    last.committer <- as.character(git$V4[i])
  }
  timestamp[i] <- last.timestamp
  commit[i] <- last.commit
  committer[i] <- last.committer
}
time <- ISOdatetime(1970,1,1,0,0,0, tz="GMT") + timestamp

df <- data.frame(git, time=time, commit=commit, committer=committer)
df <- subset(df, V2=="FILE")
changes <- data.frame(entity=df$V3, lines=as.numeric(df$V4), source=df$V1, time=df$time, commit=df$commit, committer=df$committer)
changes <- changes[with(changes, order(time)),]

git.sources <- unique(as.vector(changes$source))
```

### All changes

```{r}
showTable(changes)
```

### Changes by committer

```{r}
committers <- unique(as.vector(changes$committer))

changes.subset <- function(committer0=NULL, source0) {
  df <- if (is.null(committer0)) changes
  else subset(changes, committer==committer0)
  
  if (source0 == "all sources") df
  else subset(df, source==source0)
}
```

There are **`r num(length(committers))` committers** in the log, responsible for the following cumulative changes.

```{r}
get.totals.by.author <- function(source) {
  data.frame(committer=committers,
    commits=sapply(committers, function(c) {
        num(length(unique(changes.subset(c,source)$commit)))
      }),
    entities=sapply(committers, function(c) {
      num(length(unique(changes.subset(c,source)$entity)))
      }),
    lines=sapply(committers, function(c) {
      num(sum(as.vector(as.numeric(changes.subset(c,source)$lines))))
    }))
}

sources <- c("all sources", git.sources)
```

```{r}
renderTable({get.totals.by.author(get.agg.by.committer.source())})
selectInput("agg.by.committer.source", label=NULL, choices=sources)
get.agg.by.committer.source <- reactive({
  input$agg.by.committer.source
})
```

### Aggregate changes over time

```{r}
library(ggplot2)

day <- 60*60*24; week <- day*7; month <- day*30
min.t <- min(changes$time)
max.t <- max(changes$time)

breaks <- seq(min.t, max.t + month, by="months")
labels <- sapply(breaks[1:(length(breaks)-1)], function(t) { format(t, format="%Y-%m") })

get.plot.data <- function(source) {
  plot.data <- {}
  for (cm in committers) {
    ct <- hist(subset(changes.subset(NULL, source), committer==cm)$time, breaks=breaks, plot=FALSE)$counts
    df <- data.frame(time=labels, committer=cm, entities=ct)
    plot.data <- rbind(plot.data, df)
  }
  plot.data
}
```

The following plot shows the number of entities changed by each committer over time. The y-axis is rendered on a log scale, as some commits tend to be much larger than others.

```{r}
renderPlot({
  source <- get.hist.by.committer.source()
  ggplot(get.plot.data(source), aes(x=factor(time), y=entities)) + 
    geom_bar(stat="identity", position="dodge", aes(fill = committer)) +
    scale_y_log10() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
})
selectInput("hist.by.committer.source", label=NULL, choices=sources)
get.hist.by.committer.source <- reactive({
  input$hist.by.committer.source
})
```

### Preparing the data for this page

Create the data file `r git.log.file` by executing the script below, first setting the Bash variables for the input and output directories appropriately.

```bash
# the path to the smsn repository. The "dashboard" subdirectory should appear under this.
SMSN_HOME=...
# the path to your data; the Git directories from which you would like to extract logs should appear under this.
DATA_HOME=...

OUT_FILE=${SMSN_HOME}/dashboard/data/git-log.csv

mkdir -p ${SMSN_HOME}/dashboard/data
echo "" > ${OUT_FILE}
cd ${DATA_HOME}
for DIR in `echo */ | tr '/' '\n'`; do
  if [ -e ${DIR}/.git ]; then
      echo "adding Git log for "${DIR}
      cd ${DIR}
      git log --stat --pretty=format:"COMMIT,%h,%an,%at" \
  | grep "COMMIT\|[-+]$" | sed 's/^COMMIT/'${DIR}',COMMIT/' | sed 's/^ /'${DIR}',FILE,/' | sed 's/\.smsn//' | sed 's/  *\|  */,/' | sed 's/ [-+][-+]*$/,/' \
  >> ${OUT_FILE}
      cd ..
  fi
done
```
